### 2013-11-11 research/paper/figure/time_history_msar_mass.tex
uploaded 12.01 11/11 2013

  \caption{ Time histories of displacement and velocity at \reynoldsnumber=22300, \ustar=175 and $\frac{c}{\rho\mathcal{A}U}=9.3\times10^{-1}$. The velocity time histories are presented for: (a) $m^*=1164$; (b) $m^*=10$; (c) $m^*=5$. The time history of displacement are presented for: (a) $m^*=1164$; (b) $m^*=10$; (c) $m^*=5$   As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal and the displacement signal tend to move towards a triangular signal due to reduction in inertia.}

>>>>

  \caption{ Time histories of displacement and velocity at \reynoldsnumber=22300, \ustar=175 and $\frac{c}{\rho\mathcal{A}U}=9.3\times10^{-1}$. The velocity time histories are presented for: (a) $m^*=1164$; (b) $m^*=10$; (c) $m^*=5$. The time histories of displacement are presented for: (d) $m^*=1164$; (e) $m^*=10$; (f) $m^*=5$   As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal and the displacement signal tend to move towards a triangular signal due to reduction in inertia.}
